\section{Introduction}
\label{sec:introduction}

%\emph{What problem are you trying to solve? Why is this important? What are the main results/accomplishments/highlights of the paper. Since the reader is assumed to be familiar with the details and goal of the programming project, this section will probably be fairly short. But you can use it to briefly describe the type of solution you have chosen and why.}

This paper documents and presents our solution to the programming project.
Our first attempt to solve the project was based on a partial-order planner for atomic plans.
Our thoughts were that we could use the planner to re-plan if conflicts arose.
However, we abandoned this solution as it would simply give us a backwards breadth-first search. 
As such we aimed for developing a better solution.
For the programming language used to develop our client, we have chosen Python.

Our solution is a single-agent online centralised multibody planner, where we attempt to prioritise the order in which goals are fulfilled.
Paths were constructed in a hierarchical fashion using the weighted A* search algorithm in a relaxed domain.
In this paper we showcase the resulting performance of our client and discuss its strengths, weaknesses, and potential ways for improvement.
%We present our own goal prioritisation solution and experiment with different types of prioritisations.
%Furthermore, we used the A* search algorithm to find movement paths, for which we incorporated the ignore preconditions heuristics to find paths in a relaxed domain.

\subsection{Problem Statement}

The aim of the project is to complete a level by moving boxes to their respective goal positions.
Challenges such as coordinating agent movement, resolving conflicting movement, communication between agents, moving obstacles from a path to reach a desired destination, etc. must be handled properly for the level to be solved.
If they are left unresolved the client may never be able to find a solution.

Similar automated clients could be useful in many scenarios where repetitive work is needed.
This could for instance be in a hospital where automated agents would be responsible for porting empty hospital beds to a destination where they are needed.


\input{content/background}
\input{content/related-work}
